\chapter{Other Published Work}

Below is a list of peer-reviewed work I contributed to during the writing of this dissertation.

\begin{itemize}

\item Hendershot, J. N., Smith, J. R., Anderson, C. B., Letten, A. D., Frishkoff, L. O., Zook, J. R., Fukami, T. \& Daily, G. C. (2020). Intensive farming drives long-term shifts in avian community composition. \textit{Nature}, 579(7799), 393-396.

\item Bratman, G. N., Anderson, C. B., Berman, M. G., Cochran, B., De Vries, S., Flanders, J., Folke, C., Frumkin, H., Gross, J. J., Hartig, T., Kahn, Jr., P. H., Kuo, M., Lawler, J. J., Levin, P. S., Lindahl, T., Meyer-Lindenberg, A., Mitchell, R., Ouyang, Z., Roe, J., Scarlett, L., Smith, J. R., van den Bosch, M., Wheeler, B. W., White, M., Zheng, H. \&  Daily, G. C. (2019). Nature and mental health: An ecosystem service perspective. \textit{Science advances}, 5(7), eaax0903.

\item Ramirez-Reyes, C., Brauman, K. A., Chaplin-Kramer, R., Galford, G. L., Adamo, S. B., Anderson, C. B., Allington, G. R., Bagstad, K. J., Coe, M. T., Cord, A. F., Dee, L.E., Gould, R. K., Jain, M., Kowal, V. A., Muller-Karger, F., Norriss, J., Potapov, P., Qiu, J., Rieb, J. T.,, Robinson, B. E., Samberg, L. H., Singh, N., Szeto, S. H., Voigt, B., Watson, K. \& Wright, T. M (2019). Reimagining the potential of Earth observations for ecosystem service assessments. \textit{Science of the Total Environment}, 665, 1053-1063.

\item Smith, J. R., Letten, A. D., Ke, P. J., Anderson, C. B., Hendershot, J. N., Dhami, M. K., Dlott, G. A., Grainger, T. N., Howard, M. E., Morrison, B. M. L., Routh, D., San Juan, P. A., Mooney, H. A., Mordecai, E. A., Crowther, T. W., \& Daily, G. C. (2018). A global test of ecoregions. \textit{Nature Ecology \& Evolution}, 2(12), 1889-1896.

\end{itemize}